---
title: "nestling growth"
author: "Desiree Narango"
date: "February 26, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyr)
library(nlme)
library(ggplot2)
library(AICcmodavg)
```

#Chickadee data
# Using the methods from Sofaer  et al 2013

## To Do:
## What about including date as an effect? I wonder if I'm not seeing an effect because I'm not including that...
## The random effect of nest should take care of nest level effects like clutch size

```{r import data}

nestlings<-read.csv("C:/Users/dnarango/Documents/FINAL DATA/nestlinggrowth_allyears_2march2018.csv",
                    na.strings=".") %>%
  filter(species=="cach")

plants<-read.csv("C:/Users/dnarango/Desktop/veg_test/results/origin_importancevalues_NN_results_2018-01-27_format.csv")



## fix some minor things
nestlings[which(nestlings$band_number=="2710-25980", arr.ind = TRUE),c(17)]<-7.50


## format data
early<-nestlings %>%select(site, nest, band_number, year, date_early, broodsize_early,age_day, mass:wing) %>%
  rename(caldate=date_early, broodsize=broodsize_early) %>%
  mutate(measurement_type="early")
late<-nestlings%>%select(site, nest, band_number, year, date_late, broodsize_late, age_late, mass_late:wing_late) %>%
      rename(caldate=date_late, broodsize=broodsize_late,age_day=age_late,mass=mass_late, wing=wing_late, tarsus=tarsus_late, 
             primary_pin=primary_pin_late, primary_exposed=primary_exposed_late,
             rectrix_pin=rectrix_pin_late, rectrix_exposed=rectrix_exposed_late) %>%
  mutate(measurement_type="late")

early_late_format<-rbind(early,late)%>%
  filter(age_day!="NA") %>%
  gather(measurement, value, 8:14) %>%
  mutate(age=round(age_day)) %>%
  #filter(age<15 & age>2) %>%
  left_join(plants, by="site") %>%
  mutate(site_type=ifelse(proportion_exotic<0.5,"native","exotic")) %>%
  filter(site_type!="NA")


tarsus_growth<-early_late_format %>%
  filter(measurement=="tarsus") %>%
  select(site_type,site,nest,age_day,caldate,band_number,measurement,value,broodsize,proportion_exotic) %>%
  filter(value!="NA")%>%
  rename(site_name=site) %>%
  mutate(site=ifelse(site_type=="native",1,0)) %>%
  rename(Age=age_day)



wing_growth<-early_late_format %>%
  filter(measurement=="wing") %>%
  select(site_type,site,nest,age_day,caldate,band_number,measurement,value,broodsize,proportion_exotic) %>%
  filter(value!="NA")%>%
  rename(site_name=site) %>%
  mutate(site=ifelse(site_type=="native",1,0)) %>%
  rename(Age=age_day)


primary_growth<-early_late_format %>%
  filter(measurement=="primary_exposed") %>%
  select(site_type,site,nest,age_day,caldate,band_number,measurement,value,broodsize,proportion_exotic) %>%
  filter(value!="NA")%>%
  rename(site_name=site) %>%
  mutate(site=ifelse(site_type=="native",1,0)) %>%
  rename(Age=age_day)


mass_growth<-early_late_format %>%
  filter(measurement=="mass") %>%
  select(site_type,site,nest,age_day,caldate,band_number,measurement,value,broodsize, proportion_exotic, proportion_exotic, proportion_exotic) %>%
  filter(value!="NA")%>%
  rename(site_name=site) %>%
  mutate(site=ifelse(site_type=="native",1,0)) %>%
  rename(Age=age_day)
```
## Functions needs to run the nlme model
```{r}
## Model with no covariates
Cov0 = function(Age, Asym.int, xmid.int, K.int){
   (Asym.int)/(1 + exp(((xmid.int) - Age)*(K.int)))
}

## Derivatives (0 covariates)
DerivCov0 = deriv(body(Cov0)[[2]], namevec = c("Asym.int", "xmid.int", "K.int"), function.arg = Cov0)


##Model with 1 covariate
Cov1 = function(Age, Asym.int, Asym.beta1, xmid.int, xmid.beta1, K.int, K.beta1, covariable1){
   (Asym.int + Asym.beta1*covariable1)/(1 + exp(((xmid.int+xmid.beta1*covariable1) - Age)*(K.int+K.beta1*covariable1)))
}

## Derivatives (1 covariate)
DerivCov1 = deriv(body(Cov1)[[2]], namevec = c("Asym.int", "Asym.beta1", "xmid.int", "xmid.beta1", "K.int", "K.beta1"), function.arg = Cov1)

```


## First need to determine what model best fits the data
## steps: 
## 1. Use AIC to find best model with different random effects
## 2. Use JAGS to make predictions
```{r}
##tarsus
# Starting values:
startCov1 = c(Asym.int = 19, Asym.beta1 = 0, xmid.int = 8, xmid.beta1 = 0,  K.int = .35, K.beta1 = 0)
startCov0 = c(Asym.int = 19, xmid.int = 8, K.int = .5)


### Intercept model

## No random effects
m0 = gnls(value~ Asym.int/(1 + exp((xmid.int - Age)*K.int)), data = tarsus_growth, start = startCov0)
summary(m0)


Cand.models <- list( )
## one random effect (nest)
m1 =  nlme(value ~ SiteNATIVEDeriv(Age, proportion_exotic,Asym, xmid, K, 
                                   Kdiff, middiff, Adiff), 
                                    fixed = Asym + xmid + K +
                                    Kdiff + middiff + Adiff ~ 1, 
                                    random = K ~ 1 | nest, 
                                    data =tarsus_growth, 
                                    start = startsiteNATIVE,control=list(tolerance=100))

m2 =  nlme(value ~ SiteNATIVEDeriv(Age, proportion_exotic,Asym, xmid, K, 
                                   Kdiff, middiff, Adiff), 
                                    fixed = Asym + xmid + K +
                                    Kdiff + middiff + Adiff ~ 1, 
                                    random = Asym ~ 1 | nest, 
                                    data =tarsus_growth, 
                                    start = startsiteNATIVE,control=list(tolerance=100))

m3 =  nlme(value ~ SiteNATIVEDeriv(Age, proportion_exotic,Asym, xmid, K, 
                                   Kdiff, middiff, Adiff), 
                                    fixed = Asym + xmid + K +
                                    Kdiff + middiff + Adiff ~ 1, 
                                    random = xmid ~ 1 | nest, 
                                    data =tarsus_growth, 
                                    start = startsiteNATIVE,control=list(tolerance=100))

#1 random effect (band number)
m4 =  nlme(value ~ SiteNATIVEDeriv(Age, proportion_exotic,Asym, xmid, K, 
                                   Kdiff, middiff, Adiff), 
                                    fixed = Asym + xmid + K +
                                    Kdiff + middiff + Adiff ~ 1, 
                                    random = xmid ~ 1 | band_number, 
                                    data =tarsus_growth, 
                                    start = startsiteNATIVE,control=list(tolerance=100))
m5 =  nlme(value ~ SiteNATIVEDeriv(Age, proportion_exotic,Asym, xmid, K, 
                                   Kdiff, middiff, Adiff), 
                                    fixed = Asym + xmid + K +
                                    Kdiff + middiff + Adiff ~ 1, 
                                    random = K ~ 1 | band_number, 
                                    data =tarsus_growth, 
                                    start = startsiteNATIVE,control=list(tolerance=100))
m6 =  nlme(value ~ SiteNATIVEDeriv(Age, proportion_exotic,Asym, xmid, K, 
                                   Kdiff, middiff, Adiff), 
                                    fixed = Asym + xmid + K +
                                    Kdiff + middiff + Adiff ~ 1, 
                                    random = Asym ~ 1 | band_number, 
                                    data =tarsus_growth, 
                                    start = startsiteNATIVE,control=list(tolerance=100))

#2 random effect (nest, band number)
m7 =  nlme(value ~ SiteNATIVEDeriv(Age, proportion_exotic,Asym, xmid, K, 
                                   Kdiff, middiff, Adiff), 
                                    fixed = Asym + xmid + K +
                                    Kdiff + middiff + Adiff ~ 1, 
                                    random = Asym ~ 1 | nest/band_number, 
                                    data =tarsus_growth, 
                                    start = startsiteNATIVE,control=list(tolerance=100))

m8 =  nlme(value ~ SiteNATIVEDeriv(Age, proportion_exotic,Asym, xmid, K, 
                                   Kdiff, middiff, Adiff), 
                                    fixed = Asym + xmid + K +
                                    Kdiff + middiff + Adiff ~ 1, 
                                    random = K ~ 1 | nest/band_number, 
                                    data =tarsus_growth, 
                                    start = startsiteNATIVE,control=list(tolerance=100))
m9 =  nlme(value ~ SiteNATIVEDeriv(Age, proportion_exotic,Asym, xmid, K, 
                                   Kdiff, middiff, Adiff), 
                                    fixed = Asym + xmid + K +
                                    Kdiff + middiff + Adiff ~ 1, 
                                    random = xmid ~ 1 | nest/band_number, 
                                    data =tarsus_growth, 
                                    start = startsiteNATIVE,control=list(tolerance=100))

## random effect on multiple parameters
m9 =  nlme(value ~ SiteNATIVEDeriv(Age, proportion_exotic,Asym, xmid, K, 
                                   Kdiff, middiff, Adiff), 
                                    fixed = Asym + xmid + K +
                                    Kdiff + middiff + Adiff ~ 1, 
                                    random = Asym+ xmid ~ 1 | nest/band_number, 
                                    data =tarsus_growth, 
                                    start = startsiteNATIVE,control=list(tolerance=100))

m10 =  nlme(value ~ SiteNATIVEDeriv(Age, proportion_exotic,Asym, xmid, K, 
                                   Kdiff, middiff, Adiff), 
                                    fixed = Asym + xmid + K +
                                    Kdiff + middiff + Adiff ~ 1, 
                                    random = Asym+ K ~ 1 | nest/band_number, 
                                    data =tarsus_growth, 
                                    start = startsiteNATIVE,control=list(tolerance=100))
m11 =  nlme(value ~ SiteNATIVEDeriv(Age, proportion_exotic,Asym, xmid, K, 
                                   Kdiff, middiff, Adiff), 
                                    fixed = Asym + xmid + K +
                                    Kdiff + middiff + Adiff ~ 1, 
                                    random = xmid+ K ~ 1 | nest/band_number, 
                                    data =tarsus_growth, 
                                    start = startsiteNATIVE,control=list(tolerance=100))
m12 =  nlme(value ~ SiteNATIVEDeriv(Age, proportion_exotic,Asym, xmid, K, 
                                   Kdiff, middiff, Adiff), 
                                    fixed = Asym + xmid + K +
                                    Kdiff + middiff + Adiff ~ 1, 
                                    random = Asym+ xmid ~ 1 | nest, 
                                    data =tarsus_growth, 
                                    start = startsiteNATIVE,control=list(tolerance=100))

m13 =  nlme(value ~ SiteNATIVEDeriv(Age, proportion_exotic,Asym, xmid, K, 
                                   Kdiff, middiff, Adiff), 
                                    fixed = Asym + xmid + K +
                                    Kdiff + middiff + Adiff ~ 1, 
                                    random = Asym+ K ~ 1 | nest, 
                                    data =tarsus_growth, 
                                    start = startsiteNATIVE,control=list(tolerance=100))
m14 =  nlme(value ~ SiteNATIVEDeriv(Age, proportion_exotic,Asym, xmid, K, 
                                   Kdiff, middiff, Adiff), 
                                    fixed = Asym + xmid + K +
                                    Kdiff + middiff + Adiff ~ 1, 
                                    random = xmid+ K ~ 1 | nest, 
                                    data =tarsus_growth, 
                                    start = startsiteNATIVE,control=list(tolerance=100))
m15 =  nlme(value ~ SiteNATIVEDeriv(Age, proportion_exotic,Asym, xmid, K, 
                                   Kdiff, middiff, Adiff), 
                                    fixed = Asym + xmid + K +
                                    Kdiff + middiff + Adiff ~ 1, 
                                    random = Asym+ xmid ~ 1 | band_number, 
                                    data =tarsus_growth, 
                                    start = startsiteNATIVE,control=list(tolerance=100))

m16 =  nlme(value ~ SiteNATIVEDeriv(Age, proportion_exotic,Asym, xmid, K, 
                                   Kdiff, middiff, Adiff), 
                                    fixed = Asym + xmid + K +
                                    Kdiff + middiff + Adiff ~ 1, 
                                    random = Asym+ K ~ 1 | band_number, 
                                    data =tarsus_growth, 
                                    start = startsiteNATIVE,control=list(tolerance=100))
m17 =  nlme(value ~ SiteNATIVEDeriv(Age, proportion_exotic,Asym, xmid, K, 
                                   Kdiff, middiff, Adiff), 
                                    fixed = Asym + xmid + K +
                                    Kdiff + middiff + Adiff ~ 1, 
                                    random = xmid+ K ~ 1 | band_number, 
                                    data =tarsus_growth, 
                                    start = startsiteNATIVE,control=list(tolerance=100))

tarsus_GroupedNestNestling = groupedData(value ~ Age | nest/band_number, data =
tarsus_growth)

## correlation at band number level but not nest
m18 =  nlme(value ~ SiteNATIVEDeriv(Age, proportion_exotic,Asym, xmid, K, 
                                   Kdiff, middiff, Adiff), 
                                    fixed = Asym + xmid + K +
                                    Kdiff + middiff + Adiff ~ 1, 
                                    random = list(nest=
                                pdDiag(Asym + xmid+K ~ 1), band_number = pdSymm(Asym + xmid +K~ 1)), 
                                    data =tarsus_GroupedNestNestling, 
                                    start = startsiteNATIVE,control=list(tolerance=100))
m19 =  nlme(value ~ SiteNATIVEDeriv(Age, proportion_exotic,Asym, xmid, K, 
                                   Kdiff, middiff, Adiff), 
                                    fixed = Asym + xmid + K +
                                    Kdiff + middiff + Adiff ~ 1, 
                                    random = list(nest=
pdDiag(Asym + xmid +K ~ 1), band_number = pdDiag(Asym + xmid + K ~ 1)), 
                                    data =tarsus_GroupedNestNestling, 
                                    start = startsiteNATIVE,control=list(tolerance=100))

m20 =  nlme(value ~ SiteNATIVEDeriv(Age, proportion_exotic,Asym, xmid, K, 
                                   Kdiff, middiff, Adiff), 
                                    fixed = Asym + xmid + K +
                                    Kdiff + middiff + Adiff ~ 1, 
                                    random = list(nest=
pdDiag(Asym + xmid ~ 1), band_number = pdDiag(Asym + xmid + K ~ 1)), 
                                    data =tarsus_GroupedNestNestling, 
                                    start = startsiteNATIVE,control=list(tolerance=100))

m21 =  nlme(value ~ SiteNATIVEDeriv(Age, proportion_exotic,Asym, xmid, K, 
                                   Kdiff, middiff, Adiff), 
                                    fixed = Asym + xmid + K +
                                    Kdiff + middiff + Adiff ~ 1, 
                                    random = list(nest=
pdDiag(Asym + xmid ~ 1), band_number = pdSymm(Asym + xmid + K ~ 1)), 
                                    data =tarsus_GroupedNestNestling, 
                                    start = startsiteNATIVE,control=list(tolerance=100))

Cand.models <- list("m1" = m1,
	"m2" = m2,
		"m3" = m3,
		"m4" = m4,
		"m5" = m5,
		"m6" = m6,
		"m7" = m7,
		"m8" = m8,
		"m9" = m9,
		"m10" = m10,
		"m11" = m11,
		"m12" = m12,
		"m13" = m13,
  	"m14" = m14,
		"m15" = m15,
		"m16" = m16,
		"m17" = m17,
		"m18" = m18,
		"m19" = m19,
	  "m20" = m20,
		"m21" = m21)

library(AICcmodavg)
Modnames <- paste("mod", 1:length(Cand.models), sep = " ")
AIC<-aictab(cand.set = Cand.models, sort = TRUE, second.ord=TRUE)

AIC

```



```{r}
nlme(value ~ DerivCov1(Age, Asym.int, Asym.beta1, xmid.int, xmid.beta1, K.int, K.beta1, covariable1 = proportion_exotic), 
                  fixed = Asym.int + xmid.int + K.int + K.beta1 + xmid.beta1 + Asym.beta1 ~ 1, 
          random = K.int ~ 1 | nest/band_number, 
          data = tarsus_growth, 
          start = startCov1,
          control=list(tolerance=100))
summary(m1)
### Covariance amoung random effects
m1 = nlme(value ~ DerivCov1(Age, proportion_exotic,Asym.int, xmid.int, K.int), data = tarsus_growth, fixed = Asym.int + xmid.int + K.int ~ 1, random = list(nest =pdDiag(Asym.int + xmid.int + K.int ~ 1), band_number = pdDiag(Asym.int + xmid.int + K.int ~ 1)), start = startCov1)
summary(m1)


OnePop_NoRE_gnls = gnls(value ~ SiteNATIVEDeriv(Age, proportion_exotic,
                           Asym, xmid, K, Kdiff, middiff, Adiff), 
                        fixed = Asym + xmid + K + Kdiff + middiff + Adiff ~ 1, 
                        data = tarsus_growth, 
                        start = startsiteNATIVE)
summary(SiteNATIVE_Ai_NestNestling)

# Example syntax for models with one random effect (either Nest or Nestling) on one parameter
# Model with nest-level random effect on the asymptotic mass
OnePop_A_Nest = nlme(weight_g ~ DerivOnePop(Age, Asym, xmid, K), data = AKgrowth, fixed = Asym + xmid + K ~ 1, random = Asym ~ 1 | Nest_ID, start = startOnePop)
summary(OnePop_A_Nest)

# Model with nestling-level random effect on the inflection point
OnePop_i_Nestling = nlme(weight_g ~ DerivOnePop(Age, Asym, xmid, K), data = AKgrowth,
fixed = Asym + xmid + K ~ 1, random = xmid ~ 1 | Nestling_ID, start = startOnePop)
summary(OnePop_i_Nestling)

# Example syntax for models with both levels of random effects (Nest and Nestling) on a single parameter. Note that Nestling_ID is nested within Nest_ID.
# Model with nest- and nestling-level random effects on the inflection point
OnePop_i_NestNestling = nlme(weight_g ~ DerivOnePop(Age, Asym, xmid, K), data =
AKgrowth, fixed = Asym + xmid + K ~ 1, random = xmid ~ 1 | Nest_ID/Nestling_ID, start =
startOnePop)
summary(OnePop_i_NestNestling)

# Example syntax for models with one level of random effect on multiple parameters. By default, nlme allows for covariance between parameters.
# Model with nestling-level random effects on the asymptotic mass and the inflection point
OnePop_Ai_Nestling = nlme(weight_g ~ DerivOnePop(Age, Asym, xmid, K), data =
AKgrowth, fixed = Asym + xmid + K ~ 1, random = Asym + xmid ~ 1 | Nestling_ID, start =
startOnePop)
summary(OnePop_Ai_Nestling)

# Example syntax for models with both levels of random effects on multiple parameters.
# Model with nest- and nestling-level random effects on the asymptotic mass and the inflection point
OnePop_Ai_NestNestling = nlme(weight_g ~ DerivOnePop(Age, Asym, xmid, K), data =
AKgrowth, fixed = Asym + xmid + K ~ 1, random = Asym + xmid ~ 1 | Nest_ID/Nestling_ID,
start = startOnePop)
summary(OnePop_Ai_NestNestling)


```

###### Example syntax for producing diagnostic plots #######
```{r}
# "." references the fitted object
# Example code based on top AK model:
plot(AK_AiNestNestling_noCovBoth) # plot residuals vs. fitted values
plot(AK_AiNestNestling_noCovBoth, resid(., type = "p") ~ fitted(.) | Younger_1ifknown) #residuals vs. fitted by group - use to compare residuals of older/younger birds, populations

# observed vs. fitted values
plot(AK_AiNestNestling_noCovBoth, weight_g ~ fitted(.))
plot(AK_AiNestNestling_noCovBoth, weight_g ~ fitted(.) | Nest_ID) # separately by nest

# normal plots of residuals
qqnorm(AK_AiNestNestling_noCovBoth, ~ resid(., type = "p"))
qqnorm(AK_AiNestNestling_noCovBoth, ~ resid(., type = "p") | Younger_1ifknown)

# Check assumption that random effects are normally distributed
ranef(AK_AiNestNestling_noCovBoth, level = "Nest_ID") # this is how to access the 'BLUPs'
qqnorm(AK_AiNestNestling_noCovBoth, ~ ranef(., level = "Nest_ID"))
qqnorm(AK_AiNestNestling_noCovBoth, ~ ranef(., level = "Nestling_ID"))

# residuals by group (i.e. by nest):
plot(AK_AiNestNestling_noCovBoth, Nest_ID ~ resid(., type = "p"), abline = 0)
```

###############################################################
# Comparison of growth trajectories between two populations
###############################################################
```{r}
# Goal is to test for differences in the three logistic growth parameters between two populations.
# Model included a fixed runt effect on the inflection point that does not differ between populations (called runt)

# Function including differences between populations and a runt effect on the inflection point
SiteNATIVE_function = function(Age, site,  Asym, xmid, K, Kdiff, middiff, Adiff){
(Asym + Adiff*site)/(1 + exp(((xmid+middiff*site) -
Age)*(K+Kdiff*site)))
}

# Calculate derivatives:
SiteNATIVEDeriv = deriv(body(SiteNATIVE_function)[[2]], namevec = c("Asym", "xmid", "K",
"Kdiff", "middiff", "Adiff"), function.arg= SiteNATIVE_function)

# Starting values:
startsiteNATIVE = c(Asym = 17, xmid = 8, K = 0.5, Kdiff=0, middiff=0, Adiff = 0)


# Syntax for running models mirrors syntax shown above, with updated fixed-effect function
# Top-ranked model: Random effects of nest and nestling on the asymptotic mass and the inflection point
SiteNATIVE_Ai_NestNestling = nlme(value ~ SiteNATIVEDeriv(Age, site,
 Asym, xmid, K, Kdiff, middiff, Adiff), fixed = Asym + xmid + K +
Kdiff + middiff + Adiff  ~ 1, random = xmid ~ 1 | nest/band_number, data =
tarsus_growth, start = startsiteNATIVE,control=list(tolerance=100))
summary(SiteNATIVE_Ai_NestNestling)

### No difference in tarsus growth



### graph
newdata=expand.grid(Age=c(1:16), site=c(1,0), nest=mass_growth$nest, 
                    band_number=tarsus_growth$band_number)

newdata$predictions<-predict(SiteNATIVE_Ai_NestNestling,newdata=newdata)

newdata$site<-as.factor(newdata$site)

newdata<-filter(newdata, predictions!="NA")


site_color=c("1"="gray20","0"="gray60")

ggplot(data=newdata, aes(x=Age, y=predictions, group=site)) +
  #geom_jitter(aes(color=site), size=0.5, alpha=0.1)+
  labs(x="Nestling Age", y="Predicted Tarsus length (in mm)", group="Site Type")+
  geom_smooth(aes(color=site), se=TRUE) + 
  scale_color_manual(values=site_color,labels=c("Nonnative","Native"))+
  theme_bestgraph

```
## mass comparison
```{r comparing mass growth}
# Starting values:
startsiteNATIVE = c(Asym = 13, xmid = 8, K = 0.5, Kdiff=0, middiff=0, Adiff = 0)


# Syntax for running models mirrors syntax shown above, with updated fixed-effect function
# Top-ranked model: Random effects of nest and nestling on the asymptotic mass and the inflection point
SiteNATIVE_Ai_NestNestling = nlme(value ~ SiteNATIVEDeriv(Age, site,
 Asym, xmid, K, Kdiff, middiff, Adiff), fixed = Asym + xmid + K +
Kdiff + middiff + Adiff  ~ 1, random = xmid ~ 1 | nest/band_number, data =
mass_growth, start = startsiteNATIVE,control=list(tolerance=100))
summary(SiteNATIVE_Ai_NestNestling)

### for mass, there is a signifigant difference in K (growth)
### In other words, how quickly they grow
### native grow faster

## also signifgant difference in A
## in other words, there  is a difference in peak
## native peak at lower weights


### graph
newdata=expand.grid(Age=c(1:16), site=c(1,0), nest=mass_growth$nest, 
                    band_number=mass_growth$band_number)

newdata$predictions<-predict(SiteNATIVE_Ai_NestNestling,newdata=newdata)

newdata$site<-as.factor(newdata$site)

newdata<-filter(newdata, predictions!="NA")


site_color=c("1"="gray20","0"="gray60")

ggplot(data=newdata, aes(x=Age, y=predictions, group=site)) +
  #geom_jitter(aes(color=site), size=0.5, alpha=0.1)+
  labs(x="Nestling Age", y="Predicted Mass (in g)", group="Site Type")+
  geom_smooth(aes(color=site), se=TRUE) + 
  scale_color_manual(values=site_color,labels=c("Nonnative","Native"))+
  theme_bestgraph
  

```

```{r comparing wing}
# Starting values:
startsiteNATIVE = c(Asym = 50, xmid = 8, K = 0.5, Kdiff=0, middiff=0, Adiff = 0)


# Syntax for running models mirrors syntax shown above, with updated fixed-effect function
# Top-ranked model: Random effects of nest and nestling on the asymptotic mass and the inflection point
SiteNATIVE_Ai_NestNestling = nlme(value ~ SiteNATIVEDeriv(Age, site,
 Asym, xmid, K, Kdiff, middiff, Adiff), fixed = Asym + xmid + K +
Kdiff + middiff + Adiff  ~ 1, random = xmid ~ 1 | nest/band_number, data =
wing_growth, start = startsiteNATIVE,control=list(tolerance=100))
summary(SiteNATIVE_Ai_NestNestling)

### for wing there is no difference


### graph
newdata=expand.grid(Age=c(1:20), site=c(1,0), nest=mass_growth$nest, 
                    band_number=wing_growth$band_number)

newdata$predictions<-predict(SiteNATIVE_Ai_NestNestling,newdata=newdata)

newdata$site<-as.factor(newdata$site)

newdata<-filter(newdata, predictions!="NA")


site_color=c("1"="gray20","0"="gray60")

ggplot(data=newdata, aes(x=Age, y=predictions, group=site)) +
  #geom_jitter(aes(color=site), size=0.5, alpha=0.1)+
  labs(x="Nestling Age", y="Predicted Wing (in mm)", group="Site Type")+
  geom_smooth(aes(color=site), se=TRUE) + 
  scale_color_manual(values=site_color,labels=c("Nonnative","Native"))+
  theme_bestgraph
```
## primary
```{r comparing wing}
# Starting values
primary_growth2<-filter(primary_growth, band_number!="eisesho_unb_1")


startsiteNATIVE = c(Asym = 15, xmid = 8, K = 0.5, Kdiff=0, middiff=0, Adiff = 0)


# Syntax for running models mirrors syntax shown above, with updated fixed-effect function
# Top-ranked model: Random effects of nest and nestling on the asymptotic mass and the inflection point
SiteNATIVE_Ai_NestNestling = nlme(value ~ SiteNATIVEDeriv(Age, site,
 Asym, xmid, K, Kdiff, middiff, Adiff), fixed = Asym + xmid + K +
Kdiff + middiff + Adiff  ~ 1, random = xmid ~ 1 | nest/band_number, data =
primary_growth2, start = startsiteNATIVE,control=list(tolerance=100))
summary(SiteNATIVE_Ai_NestNestling)




### for wing there is no difference

### No difference in primary growth

### graph
newdata=expand.grid(Age=c(1:16), site=c(1,0), nest=mass_growth$nest, 
                    band_number=primary_growth$band_number)

newdata$predictions<-predict(SiteNATIVE_Ai_NestNestling,newdata=newdata)

newdata$site<-as.factor(newdata$site)

newdata<-filter(newdata, predictions!="NA")


site_color=c("1"="gray20","0"="gray60")

ggplot(data=newdata, aes(x=Age, y=predictions, group=site)) +
  #geom_jitter(aes(color=site), size=0.5, alpha=0.1)+
  labs(x="Nestling Age", y="Predicted primary growth (in mm)", group="Site Type")+
  geom_smooth(aes(color=site), se=TRUE) + 
  scale_color_manual(values=site_color,labels=c("Nonnative","Native"))+
  theme_bestgraph
```

